An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-05-13 EconGrowth.Rnw
Change China footnote from 4.1% to 0.41%, as requested by Caleb.

\noindent $\eta_{food \rightarrow work, animals}$ and $\eta_{food \rightarrow work, workers}$ are animal and worker efficiency of converting food into energy, respectively. The animal feed-to-work conversion efficiency ($\eta_{feed \rightarrow work, animals}$ = 0.4) was taken from \citet{Warr:2012a} and assumed equal across all economies. The food-to-work efficiency for workers ($\eta_{food \rightarrow work, workers}$ = 0.2) was taken from \citet[Table~B.1]{Ayres:2010ug}. Following \citet[p.~315]{Ayres:2010ug}, an additional factor ($f_{enduse/intake}$) was included to account for workers' food energy that sustains the body's normal function as opposed to providing energy for physical labor \citep{Wirsenius:2000vi} **** Caleb needs to find a detailed source (table, equation, number, page number) in Wirsenius for this approach *****. $f_{enduse/intake}$ varies by country (Table \ref{tab:f_enduse_intake}). A similar enduse-to-intake ratio could also be applied to animal work, but it was unavailable from \citet{Wirsenius:2000vi}.\footnote{The error in exergy caused by neglecting $f_{enduse/intake}$ for animals is very small, because animal muscle exergy is a small fraction of the total energy supply to any economy, with a maximum of 4.1\% for China in 1992.}

>>>>

\noindent $\eta_{food \rightarrow work, animals}$ and $\eta_{food \rightarrow work, workers}$ are animal and worker efficiency of converting food into energy, respectively. The animal feed-to-work conversion efficiency ($\eta_{feed \rightarrow work, animals}$ = 0.4) was taken from \citet{Warr:2012a} and assumed equal across all economies. The food-to-work efficiency for workers ($\eta_{food \rightarrow work, workers}$ = 0.2) was taken from \citet[Table~B.1]{Ayres:2010ug}. Following \citet[p.~315]{Ayres:2010ug}, an additional factor ($f_{enduse/intake}$) was included to account for workers' food energy that sustains the body's normal function as opposed to providing energy for physical labor \citep{Wirsenius:2000vi} **** Caleb needs to find a detailed source (table, equation, number, page number) in Wirsenius for this approach *****. $f_{enduse/intake}$ varies by country (Table \ref{tab:f_enduse_intake}). A similar enduse-to-intake ratio could also be applied to animal work, but it was unavailable from \citet{Wirsenius:2000vi}.\footnote{The error in exergy caused by neglecting $f_{enduse/intake}$ for animals is very small, because animal muscle exergy is a small fraction of the total energy supply to any economy, with a maximum of 0.41\% for China in 1992.}
